Automating Verification of MPC Security: $\metaprot$ to $\minifed$

### 2023-07-12 popl24/hyperprop.tex
checkpoint

As discussed in Section \ref{section-related-work} previous
authors have noted connections between the traditional formulation of
the MPC security model- aka the simulator security model- and
hyperproperty-style formulations of program trace behavior
\cite{8429300,wysstar} including probabilistic noninterference. In
this Section we show for to formulate extensional properties relevant
to MPC passive security in our language model by direct appeal to
program distributions. In particular, \emph{noninterference modulo
output ($\NIMO$)} is shown to be sound for MPC passive security. In
Section \ref{section-automation} we will show how $\NIMO$ can be
automatically enforced directly via whole-program analysis, or by
automatically verifying composable, intensional properties of circuit
components.

>>>>

As discussed in Section \ref{section-related-work} previous authors
have noted connections between the traditional formulation of the MPC
security model- aka the simulator security model- and
hyperproperty-style formulations of program trace behavior
\cite{8429300,wysstar} including probabilistic noninterference. In
this Section we show how to formulate security properties in our
language model by direct appeal to program distributions. In
particular, \emph{noninterference modulo output ($\NIMO$)} is shown to
be sound for MPC passive security. In Section \ref{section-automation}
we will show how $\NIMO$ can be automatically enforced directly via
whole-program analysis, or by automatically verifying composable
properties of circuit components.
